% !TEX TS-program = xelatex
% !TEX encoding = UTF-8

%\documentclass[a4paper,10pt,oneside]{article}
\documentclass[letterpaper,10pt,oneside]{article}

% Do not stop on errors during compilation.
\nonstopmode

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{CV-Preamble.tex}

% CV Info (to be customized).
\newcommand{\CVTitle}{Dan Hill's Resume}
\newcommand{\CVNote}{CV compiled on {\today}}

% PDF settings and properties.
\hypersetup{
	pdftitle={\CVTitle},
	pdfauthor={Dan Hill},
	pdfsubject={http://danhill.us},
	pdfcreator={XeLaTeX},
	pdfproducer={},
	pdfkeywords={},
	pdfpagemode={},
	bookmarks=true,
	unicode=true,
	bookmarksopen=true,
	pdfstartview=FitH,
	pdfpagelayout=OneColumn,
	pdfpagemode=UseOutlines,
	hidelinks,
	breaklinks}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\title{Dan Hill}

\begin{subtitle}
\href{https://maps.google.com/maps?q=1+North+Avenue,+Apt+42,+Springfield,+Pennsylvania+12345,+USA}
{P.O. Box 103, 207 School Street, Martha, Oklahoma 73556, USA}
\par
\href{mailto:mail@danhill.us}
{mail@danhill.us}
\,\BulletSymbol\,
+1\,(918)\,798-3517
\,\BulletSymbol\,
\href{http://danhill.us}
{http://danhill.us}
\end{subtitle}

\begin{body}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\section
{Education}
{Education}
{PDF:Education}

\href{http://cameron.edu}
{\textbf{Cameron University}},
Lawton, Oklahoma, USA

\SmallEntryGap
Bachelor of Science (B.S.) in
\href{http://www.cameron.edu/comptech}
{Computer Science}
\hfill
\DatestampYMD{2011}{1}{15} --
\DatestampYMD{2015}{12}{15}
\begin{detail}
\BulletItem
Major Advisor: Dr. Jawad Drissi
\BulletItem
Department Advisor: Dr. Johnny G. Carroll
\end{detail}


\begin{detail}
\BulletItem
GPA: 3.620 / 4.0
\end{detail}

%\EntryGap
%\href{http://www.wosc.edu}
%{\textbf{Western Oklahoma State College}},
%Altus, Oklahoma, USA
%\par
%Transfer Program for
%\href{http://www.wosc.edu}
%{Computer Science}
%\hfill
%\DatestampYMD{2009}{08}{17} --
%\DatestampYMD{2011}{12}{15}
%\begin{detail}

%\end{detail}

%%%%%%%%%%%%%%%%%%%%%%%%%
%% RESEARCH EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Research Experience}
{Research Experience}
{PDF:ResearchExperience}

\href{http://www.example.com/my-institute}
{\textbf{Cameron University}}
\par
Undergraduate Research Student, Department of Computing and Technology
\hfill
\DatestampYMD{2015}{08}{17} --
\DatestampYMD{2015}{12}{15}
\begin{detail}
\BulletItem
Project:
Algorithms for the Online Time Dependant Freeze-Tag Problem
\BulletItem
Supervisor:
Dr. Chao Zhao
\BulletItem
Research areas:
Swarm robotics, algorithms, combinatorics.
\end{detail}

%%%%%%%%%%%%%%%%%%
%% PUBLICATIONS %%
%%%%%%%%%%%%%%%%%%

%\section
%{Publications}
%{Publications}
%{PDF:Publications}

%\subsection
%{Submitted}
%{Submitted}
%{PDF:Submitted}

%\EntryGap
%\NumberedItem{\,\,\,1}
%\href{http://github.com/dan-hill/freezetag}
%{\underline{D. Hill},
%``Algorithms for the Online Time Dependant Freeze-Tag Problem,''
%\textit{Oklahoma Journal of Undergraduate Research}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACADEMIC HONORS & AWARDS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Academic Honors\newline
\& Awards}
{Academic Honors \& Awards}
{PDF:AcademicHonorsAwards}

President's Academic Achievement Scholarship, Cameron University
\hfill
\DatestampYMD{2014}{1}{15}
\begin{detail}
	Provides a stipend and tuition waiver to selected students with a GPA 4.0 for the previous semester. 
\end{detail}

\EntryGap

President's Partners Scholarship, Cameron University
\hfill
\DatestampYMD{2012}{08}{15} 
\begin{detail}
	Provides a stipend and tuition waiver to selected students with a GPA of at least 3.0. 
\end{detail}

\EntryGap

President's List, Cameron University
\hfill
\DatestampYMD{2012}{05}{15} \& \DatestampYMD{2015}{12}{15}
\begin{detail}
	For attaining a semester GPA of at least 4.0.
\end{detail}


%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% OTHER HONORS & AWARDS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Other Honors\newline
\& Awards}
{Other Honors \& Awards}
{PDF:OtherHonorsAwards}

Mobile Applications Development Competition,
Third Prize,
AITP Region 3
\hfill
\DatestampYMD{2014}{09}{10}
\begin{detail}
Awarded at the AITP Region 3 student conference at Cameron University.
\end{detail}

\EntryGap

Database Design Competition,
Second Prize,
Technology Week
\hfill
\DatestampYMD{2014}{04}{10}
\begin{detail}
	Awarded at Cameron University during the 2014 Technology Week.
\end{detail}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PROFESSIONAL AFFILIATIONS & ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section
%{Professional Affiliations\newline
%\& Activities}
%{Professional Affiliations \& Activities}
%{PDF:ProfessionalAffiliationsActivities}


%\href{http://www.acm.org/}
%{\textbf{Association for Computing Machinery}},
%Oklahoma, USA
%\par
%Member
%\hfill
%\DatestampY{2015} --
%Present

%\EntryGap

%\href{http://www.aitp.com}
%{\textbf{Association of Information Techonology Professionals}},
%Oklahoma, USA
%\par
%Member
%\hfill
%\DatestampY{2013} --
%Present


%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% OTHER WORK EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section
{Other Work\newline
Experience}
{Other Work Experience}
{PDF:OtherWorkExperience}

\href{http://www.example.com/my-company}
{\textbf{Passpack}},
Salt Lake City, Utah, USA
\par
Test Engineer
\hfill
\DatestampYMD{2011}{06}{15} -- Present
\begin{detail}
\BulletItem
Designed and implemented over 800 automated tests in JavaScript, Scala, and Selenium. 
\end{detail}

\EntryGap

\href{http://www.example.com/my-company}
{\textbf{Comanche County Memorial Hospital}},
Lawton, Oklahoma, USA
\par
Lead Developer
\hfill
\DatestampYMD{2015}{01}{07} -- \DatestampYMD{2015}{05}{15}
\begin{detail}
\BulletItem
Led a team of 6 computer science students through a large multi-team project.
\BulletItem
Designed and developed a web-based IT Asset Tracking System featuring an Ember.js client side application and a Flask.py RESTful API server.
\end{detail}

\EntryGap

\href{http://www.example.com/my-company}
{\textbf{Cameron University Career Services}},
Lawton, Oklahoma, USA
\par
Team Leader
\hfill
\DatestampYMD{2014}{01}{07} -- \DatestampYMD{2014}{05}{15}
\begin{detail}
	\BulletItem
	Led a team of 6 computer science students through the development of an internship tracking database.
	\BulletItem
	Designed and developed a Microsoft SQL Server database and Microsoft Access front end to track internship data for Cameron University Career Services.
\end{detail}

\EntryGap

\href{http://www.example.com/my-company}
{\textbf{Lawton Marketing Group}},
Lawton, Oklahoma, USA
\par
Mobile Website Developer, SEO Specialist
\hfill
\DatestampYMD{2013}{03}{15} --\DatestampYMD{2014}{01}{15}
\begin{detail}
	\BulletItem
	Developed mobile friendly versions of Wordpress based client websites.
	\BulletItem
	Audited content and semantic structure of dozens of client websites for compliance with Google standards.
\end{detail}

%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\section
{Skills}
{Skills}
{PDF:Skills}
{\textbf{Concepts}} 
\par
Source Control, Object Oriented Programming, Functional Programming, Test Design, Database Design, Linux Administration. 
 
\EntryGap

{\textbf{Languages and Frameworks}} 
\par
C++, Python, JavaScript, Scala, Emacs Lisp, SQL, Node.js, Ember.js, SciPy, MySQL, SQLServer, Nginx,
{\LaTeX}.

\end{body}

%%%%%%%%%%%
% CV NOTE %
%%%%%%%%%%%



\end{document}
